Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-02-18 PaperVictor.tex
Version aprovada por Dra. Vivechana

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage{braket}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
%\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, we design
mirrors using \textit{chirped}-type structures and by stacking
appropriately tuned sub-mirrors, and we optimize the design parameters
to maximize the
optical reflectance $\braket{R}$ averaged within a wide
spectral range  covering the visible and near infrared regions, and
within a wide angular range. The chirped structures are found to be
more suitable for the visible range,
while stacked sub-mirrors are found to be better for the NIR
region. We design, fabricate and characterize
some of the optimized omnidirectional mirrors with less
than 100 pairs of layers. We obtained structures with a wider
omnidirectional spectral region than those previously
reported.
\end{abstract}
\notaL{No sé si Vivechna quiera añadir al ICF y mencionar su estancia
  en los agrads.}
\section{Introduction}

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
their energies are consequently organized into photonic bands. In
analogy to electronic bands withiny a
crystal, propagation is forbidden if the energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
The use of metallic
mirrors is limited due to their relatively large absorption at the
visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses corresponds to a quarter of a wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

Here we study multilayered structures where the thicknesses for each
pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
gradually with the depth of the layer, according to
\begin{equation}
\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
\end{equation}%
\notaL{Quité el -1 en el numerador pues antes pusimos que j empezaba
  en 0}
where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
maximum {\em design} wavelengths respectively, $N_p$ is the number of
periods  in the structure, and $f(\xi)$ is a smooth function that
goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
substrate ($\xi=1)$. We only consider increasing functions $f$ due to
the high absorption of PS in the ultraviolet region, which decreases in
the visible and becomes negligible in the near infrared, so, that the first
periods are tuned in the UV-Vis regions. We consider the
following classes of functions:
\begin{equation}
f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
\end{equation}
\begin{equation}
f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
\label{F2}
\end{equation}
and%
\begin{equation}
f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
\end{equation}
where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
to maximize the average reflectance $\braket{R}$ over given spectral
and angular ranges. The class
$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
increasing profiles, $f_2$ is the arithmetic mean
of two functions of the type $f_{1}$ with different
powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
designed so that the first term dominates near the surface and the
second near the substrate, to allow different behaviors
at the edges of the spectrum.
The parameters
$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
reflectance for non-polarized light $\braket{R}$ averaged in the
angular range of $0^\circ$ to $90^\circ$ and either in the
spectral region $\mathcal R_1$ from 350 to
1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
\notaL{Any reason
	for these choices? They seem arbitrary.} \notaL{Creo que alguna
	explicación  sencilla merece el lector.}
\notaV{Agregue:  }
Approximately $90\%$ of the solar radiation that reaches the
earth's surface is contained in the spectral region
$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \notaL{¿qué es
  terrestrial solar? terrestrial solar radiation} \cite{Bird1983}. A direct
application of the optimized structures in these regions is solar
reflectors. \notaL{¿Pero por qué en un caso dejasta $\lambda_{\min}$
  fijo y en el otro caso no? Sería bueno que el lector entienda todas
  las decisiones que sean fáciles de explicar}
The
optimized parameters corresponding to the choice $p_l=0.51$ and
$p_h=0.76$ for the low and high porosities
are shown in Table \ref{tab:tableA}.

@@

The function $f_{3}$ yields after optimization the highest
$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
structure. Furthermore, this
structure has an omnidirectional width (ODW) of 250 nm
centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
photonic structures have been reported with
ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
which $R>90\%$ for all angles. Here we we adopt the same criterium.
We synthesized a structure designated {\em sample $S_1$} corresponding
to these results. For the region $\mathcal R_2$ the
resulting structures have similar thicknesses and attain similar average reflectance,
though the one with the smallest thickness and the maximum $\braket{R}$
is that obtained from the family $f_{1}$. We
also synthesized the corresponding
structure and designated it {\em sample $S_2$}. The
calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
This structure has a very wide region where $R(\lambda, \theta)>
0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
from $0^\circ$ to $70^\circ$. Thus, it has a
quasi-ODW of 2150 nm centered at 1925 nm.
The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
similar. For example, for $\mathcal R_1$ the optimal photonic
structures have a small number of periods tuned to the wavelengths where
silicon has a large absorption, i.e.,  the first periods of the
structure.
As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
far from a linear profile.
\begin{figure}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=\textwidth]{F1Alternativa.pdf}
  \end{center}
  \caption{Profiles of the functions $f_n(\xi_j)$ \notaL{¿No sería
      mejor rotular el eje horizontal de (a) y (c) como $\xi$ y que
      vaya de 0 a 1? Si no, recuerda que tomamos $j$ va de 0 a $N_p-1$} optimized for
    the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
    $\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
    for non-polarized light
    vs. wavelength and angle of incidence of the structure
    optimized for the region $\mathcal R_1$ (panel b) and
    $\mathcal R_2$ (panel d). The dotted lines
    indicate the ODB and the dashed lines
    indicate the quasi-ODB.}
\end{figure}

@@

We have designed, fabricated and characterized highly reflective quasi
omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
spectral range, optimized through two techniques: chirping and
stacking of Bragg-type sub-structures. Numerical calculations were
carried out employing the transfer matrix method and we optimized the
design parameters to maximize the reflectance averaged over different spectral ranges and for
all angles. We manufactured some of the optimized structures with
porous silicon
dielectric multilayers and compared their measured  optical properties
to the results of calculations. We fabricated two chirped structures
with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm centered
at 1160 nm and 1925 nm, respectively. We fabricated a
stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
with a bandwidth of 1800 nm centered at 1850 nm.
Thus, our techniques allowed us to obtain very
good relatively thin quasi omnidirectional mirrors with wide bands
over different wavelength ranges.
\notaL{Me sospecho que lo que sigue era un poco improvisada esta respuesta, pues el
  resultado depende de la región espectral, contrastes, etc. Entiendo
  que estás contestando literalmente mi pregunta previa, pero desmerece las
  conclusiones. El lector sin experiencia se quedará en las mismas,
  además de ofendido de que te refieras en el texto a ellos
  directamente. Mejor quitémoslo:
Furthermore, if someone without experience wants to obtain an
optimized photonic structure, we recommend using the chirped type
structures. There are cases in which it is suggested to use
sub-mirror stacking, for example, when the absorption of the
materials is negligible.}
Our analysis techniques can
be used for the optimization of the reflectance multilayered PS systems with
different refractive index contrasts or for systems with other types of
materials. Such proposed structures could be used as mirrors for solar
concentrators, flat focusing reflectors, thermal regulators, or, if
defects are included, as filters or remote chemical/biosensors with a
wide angular independent response.

\section*{Acknowledgments}
This work was partially supported by Consejo Nacional de Ciencia y
Tecnolog\'{i}a through grant No. 256243, C\'{a}tedras
Conacyt program 1577, and by DGAPA-PAPIIT UNAM under grant IN111119.
HPA also express his gratitude to the Coordinaci\'{o}n
de la Investigaci\'{o}n Cient\'{i}fica de la Universidad
Michoacana de San Nicol\'{a}s de Hidalgo.
\notaL{Quizás Vivechna quiera mencionar al ICF. Quizás Victor también,
  dado que puso este artículo en su reporte sobre su estancia en el icf.}

\bibliographystyle{unsrt}
\bibliography{Bibliografia}
\end{document}

>>>>

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}

%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}

\begin{document}
	\let\WriteBookmarks\relax
	\def\floatpagepagefraction{1}
	\def\textpagefraction{.001}
	\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
	\shortauthors{V. Castillo-Gallardo et~al.}

	\title [mode = title]{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}

	\author[1,2,3]{V. Castillo-Gallardo}
	\cormark[1]
	\ead{ing.victorcg@gmail.com}
	\credit{Conceptualization, Software $\&$ Investigation, synthesis $\&$ characterization, Writing}
	\address[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
		Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
		Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
		M\'{e}xico.}

	\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
	\ead{fmatpuente@gmail.com}
	\credit{Software $\&$ Investigation}
	\address[2]{Instituto de Ciencias F\'{i}sicas, Universidad
		Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
		Col. Chamilpa, 62210 Cuernavaca, Morelos, M\'{e}xico.}
	\address[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
		Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
		Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}

	\author[4]{D. Ariza-Flores}
	\ead{david1cool@gmail.com}
	\credit{Investigation, Writing - review $\&$ editing}
	\address[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
		Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
		S.L.P., 78210, M\'{e}xico.}

	\author[3]{H\'{e}ctor P\'{e}rez-Aguilar}
	\ead{hiperezag@yahoo.com}
	\credit{Investigation and Supervision}

	\author[2]{W. Luis Moch\'{a}n}
	\ead{mochan@fis.unam.mx}
	\credit{Conceptualization, Funding acquisition, Investigation, Supervision, Writing - review $\&$ editing}

	\author[1]{V Agarwal}
	\cormark[2]
	\fnmark[1]
	\ead{vagarwal@uaem.mx}
	\credit{Conceptualization, Funding acquisition, Investigation, Methodology, Supervision, Writing - review $\&$ editing}

	\cortext[cor1]{Corresponding author}
	\cortext[cor2]{Principal corresponding author}
	\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM}

	\begin{abstract}
		Porous silicon is a very versatile material for developing optical
		devices based on multilayered structures, since high and low porosity layers
		can be synthesized by a simple electrochemical technique. In the present work, we design
		mirrors using \textit{chirped}-type structures and by stacking
		appropriately tuned sub-mirrors, and we optimize the design parameters
		to maximize the
		optical reflectance $\braket{R}$ averaged within a wide
		spectral range  covering the visible and near infrared regions, and
		within a wide angular range. The chirped structures are found to be
		more suitable for the visible range,
		while stacked sub-mirrors are found to be better for the NIR
		region. We design, fabricate and characterize
		some of the optimized omnidirectional mirrors with less
		than 100 pairs of layers. We obtained structures with a wider
		omnidirectional spectral region than those previously
		reported.
	\end{abstract}

	\begin{graphicalabstract}
		\includegraphics[width=\textwidth]{GraphicalAbstract.pdf}
	\end{graphicalabstract}

	\begin{highlights}
		\item We design, optimize, fabricate and characterize wideband quasi-omnidirectional (q-OD) structures using different approaches.
		\item Reflectance averaged over wide spectral range is optimized with simple parametrized functions (chirped) and by stacking Bragg submirrors.
		\item Chirped structure with q-OD bandwidth of 1800 nm in the NIR have been demonstrated.
		\item Stacking Bragg submirrors resulted in similar q-OD band with two third of total physical thickness.
		\item Agreement between the theoretical and experimental results is obtained for porous silicon multilayers .
		\item Proposed design techniques can be useful for obtaining OD dielectric mirrors with different materials in large spectral regions.
	\end{highlights}

	\begin{keywords}
		Optimized reflectance \sep Omnidirectional structures \sep Chirped structures \sep Stacked Bragg mirror structures
	\end{keywords}

	\maketitle

	\section{Introduction}
	Photonic crystal (PC)-based structures have been extensively investigated due
	to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
	Photons entering a PC interact with its periodically varying dielectric constant and
	their energies are consequently organized into photonic bands. In
	analogy to electronic bands withiny a
	crystal, propagation is forbidden if the energy lies
	within certain regions known as photonic band gaps (PBG's). Thus, the
	PC behaves as a mirror if illuminated by light with frequencies
	within in a PBG. For several applications it is useful to fabricate
	{\em ommnidirectional} mirrors with an absolute band gap for all angles of incidence.
	The use of metallic
	mirrors is limited due to their relatively large absorption at the
	visible (Vis) and near infrared (NIR) frequencies.  An attractive alternative
	consists of low-absorption dielectric
	structures,  which may be designed for specific frequency
	ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
	applications in optoelectronics, optical telecommunications and computing,
	laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
	\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
	of periodically alternating
	layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
	corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
	thicknesses corresponds to a quarter of a wavelength
	$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
	wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
	which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
	and the number of periods are large enough. Mirrors with high
	reflectance within a wider frequency range may be engineered by
	using different nominal wavelengths for different layers.
	One way to obtain such structures is to gradually change the width of
	the layers as a function of their depth, producing
	\textit{chirped}-type structures \cite{Zipock1997}.
	Another alternative is to stack BMs, in such a way that their reflection bands partially
	overlap each other at their edges, resulting in a wider high-reflection band \cite{Xifre2009}.

@@

	Here we study multilayered structures where the thicknesses for each
	pair $j=0\ldots N_p-1$ of layers are tuned to a wavelength $\lambda_j$ which changes
	gradually with the depth of the layer, according to
	\begin{equation}
		\lambda_{j}=\lambda_{\min }+\left(\lambda_{\max }-\lambda_{\min}\right) f\left(\frac{j}{N_p-1}\right),\label{Dis}
	\end{equation}%
	where $\lambda_{\min }$ and $\lambda_{\max }$ are the minimum and
	maximum {\em design} wavelengths respectively, $N_p$ is the number of
	periods  in the structure, and $f(\xi)$ is a smooth function that
	goes from 0 to 1 as its argument goes from the surface ($\xi=0$) to the
	substrate ($\xi=1)$. We only consider increasing functions $f$ due to
	the high absorption of PS in the ultraviolet region, which decreases in
	the visible and becomes negligible in the near infrared, so, that the first
	periods are tuned in the UV-Vis regions. We consider the
	following classes of functions:
	\begin{equation}
		f_{1}\left(\xi \right) =\xi^{\alpha },  \label{F1}
	\end{equation}
	\begin{equation}
		f_{2}\left(\xi \right) =\frac{1}{2}\left(\xi^{\alpha }+\xi^{\beta}\right)
		\label{F2}
	\end{equation}
	and%
	\begin{equation}
		f_{3}\left(\xi\right) =A\xi^{\alpha }\left(1-\xi\right) +\xi^{\beta },  \label{F3}
	\end{equation}
	where $\alpha$, $\beta$ and $A$ are parameters to optimize in order
	to maximize the average reflectance $\braket{R}$ over given spectral
	and angular ranges. The class
	$f_{1}$ (Eq. (\ref {F1})) with  $\alpha>0$ corresponds to simple
	increasing profiles, $f_2$ is the arithmetic mean
	of two functions of the type $f_{1}$ with different
	powers $\alpha$ and $\beta$, and $f_{3}$ (Eq. (\ref{F3})) is
	designed so that the first term dominates near the surface and the
	second near the substrate, to allow different behaviors
	at the edges of the spectrum.
	The parameters
	$\alpha$, $\beta$, $A$ and $N_{p}$ were optimized to maximize the
	reflectance for non-polarized light $\braket{R}$ averaged in the
	angular range of $0^\circ$ to $90^\circ$ and either in the
	spectral region $\mathcal R_1$ from 350 to
	1400 nm or $\mathcal R_2$ from 400 to 3000 nm. For $\mathcal R_1$ we took
	$\lambda_{\min}$ as another parameter to be optimized while $\lambda_{\max}$
	was fixed at 1400 nm. For $\mathcal R_2$ we fixed both
	$\lambda_{\min}=850$ nm and $\lambda_{\min}=3000$ nm.
	In the first case, we decided to optimize $\lambda_{min}$ to 
	obtain the best design in the high absorption zone of the PS.
	Approximately $90\%$ of the solar radiation that reaches the
	earth's surface is contained in the spectral region
	$\mathcal R_1$, and $98\%$ in $\mathcal R_2$ \cite{Bird1983}. 
	A direct
	application of the optimized structures in these regions is solar
	reflectors. The
	optimized parameters corresponding to the choice $p_l=0.51$ and
	$p_h=0.76$ for the low and high porosities
	are shown in Table \ref{tab:tableA}.

@@

	The function $f_{3}$ yields after optimization the highest
	$\braket{R}$ in the region $\mathcal R_1$ and with the thinnest
	structure. Furthermore, this
	structure has an omnidirectional width (ODW) of 250 nm
	centered at (ODC) 1125 nm, as shown in Fig. \ref{Fig1}(b).  Various
	photonic structures have been reported with
	ODB's \cite{Xu2018,Ahmed2014,Reiner2000} defined as those spectral regions for
	which $R>90\%$ for all angles. Here we we adopt the same criterium.
	We synthesized a structure designated {\em sample $S_1$} corresponding
	to these results. For the region $\mathcal R_2$ the
	resulting structures have similar thicknesses and attain similar average reflectance,
	though the one with the smallest thickness and the maximum $\braket{R}$
	is that obtained from the family $f_{1}$. We
	also synthesized the corresponding
	structure and designated it {\em sample $S_2$}. The
	calculated optimized reflectance spectrum is shown in Fig. \ref{Fig1}(d).
	This structure has a very wide region where $R(\lambda, \theta)>
	0.90$, which goes from 850 to 3000 nm, but in a restricted angular range
	from $0^\circ$ to $70^\circ$. Thus, it has a
	quasi-ODW of 2150 nm centered at 1925 nm.
	The functions $f_n$ optimized for the region $\mathcal R_1$ are shown
	in Fig. \ref{Fig1}(a), and those for $\mathcal R_2$
	in Fig. \ref{Fig1}(c). The profiles $f_n$ are qualitatively
	similar. For example, for $\mathcal R_1$ the optimal photonic
	structures have a small number of periods tuned to the wavelengths where
	silicon has a large absorption, i.e.,  the first periods of the
	structure.
	As withinin $\mathcal R_2$ the absorption of porous silicon is negligible, the optimized $f_n$ are not too
	far from a linear profile.
	\begin{figure}
		\label{Fig1}
		\begin{center}
			\includegraphics[width=\textwidth]{F1Alternativa.pdf}
		\end{center}
		\caption{Profiles of the functions $f_n(\xi_j)$ optimized for
			the region $\mathcal R_1$ from 350 to 1400 nm (panel a) and
			$\mathcal R_2$ from 400 to 3000 nm (panel c). Reflectance
			for non-polarized light
			vs. wavelength and angle of incidence of the structure
			optimized for the region $\mathcal R_1$ (panel b) and
			$\mathcal R_2$ (panel d). The dotted lines
			indicate the ODB and the dashed lines
			indicate the quasi-ODB.}
	\end{figure}

@@

	We have designed, optimized, fabricated and characterized highly reflective quasi
	omnidirectional (angular range of $0-60^\circ$) multilayered structures with a wide
	spectral range. Two techniques, chirping (a continuous change in thicknesses) and
	stacking of Bragg-type sub-structures, have been used to enhance the reflectance with minimum thickness for a given pair of refractive indices. Numerical calculations were
	carried out employing the transfer matrix method and we optimized the
	design parameters to obtain maximal reflectance averaged over different spectral ranges for
	all angles. We fabricated some of the optimized structures with
	porous silicon
	dielectric multilayers and compared their measured  optical properties
	with the calculations. Two chirped structures 
	with thicknesses 21.6 $\mu$m and 60.4 $\mu$m,
	resulting in quasi omnidirectional mirrors with bandwidths of 360 nm and 1800 nm, centered
	at 1160 nm and 1925 nm respectively have been shown. In addition, we fabricated a
	stacked structure  with a thickness of 41.5 $\mu$m resulting in a quasi omnidirectional mirror
	with a bandwidth of 1800 nm centered at 1850 nm.
	Thus, our techniques allowed us to obtain relatively thin quasi-omnidirectional mirrors with wide bands
	over different wavelength ranges. 
	Our analysis techniques can
	be used for the optimization of the reflectance multilayered PS systems with
	different refractive index contrasts or for systems with other types of
	materials. Such proposed structures could be used as mirrors for solar
	concentrators, flat focusing reflectors, thermal regulators, or, if
	defects are included, as filters or remote chemical/biosensors with a
	wide angular independent response.

	\section*{Acknowledgments}

	This project is supported by Consejo Nacional de Ciencia y
	Tecnolog\'{i}a through grant No.A-S1-30393(VA), 256243 (DA), C\'{a}tedras
	Conacyt program 1577 (DA), and by DGAPA-PAPIIT UNAM under grant IN111119 (LM).
	VA acknowledges PRODEP (Sabbatical grant), and
	is grateful to ICF where she spent the sabbatical year.
	HPA also expresses his gratitude to the Coordinaci\'{o}n
	de la Investigaci\'{o}n Cient\'{i}fica de la Universidad
	Michoacana de San Nicol\'{a}s de Hidalgo. VCG is grateful to CIICAp 
	and ICF where he did this work.

	\printcredits

	\bibliographystyle{unsrt}
	\bibliography{Bibliografia}

\end{document}
